---
format: gfm
execute: 
  warning: false
---

```{r}
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(tidyverse)
```

# TODOs

1. supports id conversion?
  - Use suggest, use AnnotationDbi
1. input NA should return NA
  1. Add a column for search term
  1. Two tires:
    - Query NA, meaning the conversion from symbol to entrezID failed
    - No ortholog, meaning no return
1. fix buildignore

# RDIOPT

<!-- badges: start -->
<!-- badges: end -->

RDIOPT is a simple wrapper around the [DIOPT](https://www.flyrnai.org/diopt) Ortholog Finder. The intention for this package is to allow querying orthologs from R directly, without copy and paste. 


RDIOPT relies on the [DIOPT API](https://www.flyrnai.org/tools/diopt/web/api) to query and search results.

## Installation

You can install the development version of RDIOPT from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("myuhao/RDIOPT")
```

## Example

Call `find_orthologs()` with some of your gene of interests. The function should give you a nice `tibble` with all the relevant information.

:::{.callout-note}
Note that currently DIOPT API only supports **Entrez ID**. You will need to convert your genes accordingly.
:::

```{r example}
library(RDIOPT)

gene_of_interests = c(1232, 7316)
orthologs = find_orthologs(gene_of_interests, from = 9606, to = 7227, filter = "none")
colnames(orthologs)
```

The result table has many relevant information, but it can be summarized in to three categories:

1. Function parameters.
1. Source gene information.
1. Target gene information.


#### Function parameters

DIOPT recorded the following parameter used for the query:
```{r}
#| echo: false
orthologs[c(1:3, 10)]
```

#### Source gene information

DIOPT will try to find information of the gene you submitted.
```{r}
#| echo: false
orthologs[4:9]
```
#### Source gene information

Here is the actual ortholog information. Fileds are left `NA` in case no orthologs can be found.
```{r}
#| echo: false
orthologs[11:27]
```

## Reference
